---
title: "Arrows_stats"
author: "Eliany Perez"
date: "4/19/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/12393/Desktop/Arrows")
roi<-read.csv("ROIs.csv")
```

```{r}
#ttests

jmv::ttestOneS(
  data = roi,
  vars = Parietal,
  meanDiff = TRUE,
  ci = TRUE,
  effectSize = TRUE,
  ciES = TRUE,
  desc = TRUE)

jmv::ttestOneS(
  data = roi,
  vars = Lateral.Occipital,
  meanDiff = TRUE,
  ci = TRUE,
  effectSize = TRUE,
  ciES = TRUE,
  desc = TRUE)

```

Because the previous ttests were done on a large region of the brain, I extracted specific coordinates based on previous studies to conduct the following ttests and now we can see that they are statistically significant.

```{r}

#Left Parietal
jmv::ttestOneS(
  data = roi,
  vars = Left.Parietal,
  meanDiff = TRUE,
  ci = TRUE,
  effectSize = TRUE,
  ciES = TRUE,
  desc = TRUE)


#right Parietal
jmv::ttestOneS(
  data = roi,
  vars = Right.Parietal,
  meanDiff = TRUE,
  ci = TRUE,
  effectSize = TRUE,
  ciES = TRUE,
  desc = TRUE)

```
So now we know that for words versus images, there is significant activation in both the left and right parietal cortex.

```{r}
library(ggplot2)

ggplot(roi, aes(words_LP, images_LP, color= ID)) + 
  geom_point()+
  geom_smooth(method = lm)
```

```{r}
library(ggplot2)

ggplot(roi, aes(words_RP, images_RP, color= ID)) + 
  geom_point()+
  geom_smooth(method = lm)
```
Both for the Left and Right Parietal cortex, there as activation increases for images, activation for words decreases.